Autoregressive example

### 2020-08-04 src/s_ar1.Rmd
finished run through draft incorporating Aki's comments

nreplicates <- 50
lnum_chains <- c(32)
mResults <- matrix(nrow = nreplicates * length(lnum_chains),
                   ncol = 4)
k <- 1
for(j in seq_along(lnum_chains)){
  print(j)
  for(i in 1:nreplicates){
    temp <- f_replicate_n(lnum_chains[j])
    mResults[k, ] <- c(lnum_chains[j], i, temp$r_star, temp$r_hat)
    k <- k + 1
  }
  # saveRDS(mResults, "../data/ar1_numchains_extra2.rds")
}

colnames(mResults) <- c("nchains", "iterate", "R*", "split-Rhat")
mResults <- as.data.frame(mResults) %>% 
  filter(nchains < 64)
saveRDS(mResults, "../data/ar1_numchains.rds")
mResults <- readRDS("../data/ar1_numchains.rds")
b_sum <- mResults %>% 
  melt(id.vars=c("nchains", "iterate")) %>%
  group_by(nchains, variable) %>% 
  summarise(lower=quantile(value, 0.25),
         upper=quantile(value, 0.75),
         middle=quantile(value, 0.5))

g <- mResults %>% 
  melt(id.vars=c("nchains", "iterate")) %>% 
  left_join(b_sum, by = c("nchains", "variable")) %>% 
  ggplot(aes(x=as.factor(nchains), y=value)) +
  geom_jitter(width = 0.2, colour="grey") +
  geom_pointrange(aes(ymin=lower, y=middle, ymax=upper)) +
  facet_wrap(~variable) +
  scale_x_discrete() +
  xlab("# chains") +
  ylab("Value") +
  scale_color_grey() +
  theme(axis.text = element_text(colour="black", size=12),
        axis.title = element_text(colour="black", size=14),
        strip.text.x = element_text(colour="black", size=14),
        legend.position = "none")
ggsave("../output/ar1_numchains.pdf", g, width = 8, height = 4)
```

>>>>

nreplicates <- 50
lnum_chains <- c(2, 4, 6, 8, 16, 32)
mResults <- matrix(nrow = nreplicates * length(lnum_chains),
                   ncol = 4)
k <- 1
for(j in seq_along(lnum_chains)){
  print(j)
  for(i in 1:nreplicates){
    temp <- f_replicate_n(lnum_chains[j])
    mResults[k, ] <- c(lnum_chains[j], i, temp$r_star, temp$r_hat)
    k <- k + 1
  }
}

colnames(mResults) <- c("nchains", "iterate", "R*", "split-Rhat")
mResults <- as.data.frame(mResults) %>% 
  filter(nchains < 64)
saveRDS(mResults, "../data/ar1_numchains.rds")
mResults <- readRDS("../data/ar1_numchains.rds") %>% 
  filter(iterate<=50)
b_sum <- mResults %>% 
  melt(id.vars=c("nchains", "iterate")) %>%
  group_by(nchains, variable) %>% 
  summarise(lower=quantile(value, 0.25),
         upper=quantile(value, 0.75),
         middle=quantile(value, 0.5))

g <- mResults %>% 
  melt(id.vars=c("nchains", "iterate")) %>% 
  left_join(b_sum, by = c("nchains", "variable")) %>% 
  ggplot(aes(x=as.factor(nchains), y=value)) +
  geom_jitter(width = 0.2, colour="grey") +
  geom_pointrange(aes(ymin=lower, y=middle, ymax=upper)) +
  facet_wrap(~variable) +
  scale_x_discrete() +
  xlab("# chains") +
  ylab("Value") +
  scale_color_grey() +
  theme(axis.text = element_text(colour="black", size=12),
        axis.title = element_text(colour="black", size=14),
        strip.text.x = element_text(colour="black", size=14),
        legend.position = "none")
ggsave("../output/ar1_numchains.pdf", g, width = 8, height = 4)

```
